---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SCOPEr

<!-- badges: start -->
<!-- badges: end -->

The goal of SCOPEr is to run SCOPE model in R language so that you can properly document your model configuration runs

## Installation

You can install the development version of SCOPEr from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("kacebron/SCOPEr")
```

## Verification run

This is an initial run of SCOPE using function run_scope() to test the integrity of the copy of your model.
If output is the same as the verification dataset, it means that your model is intact and working good.

```{r example}
library(SCOPEr)

run_scope(SCOPE_path = "~/Documents/1_postdoc_projects/1_serc_nasa_roses/02_projects/SCOPE/SCOPE.m") # copy the filepath where SCOPE.m is located in your computer then paste it as the SCOPE_path argument
```

## Turn off simulation mode

```{r}
set_options(verify = FALSE)
```

## Select simulation mode: 0 = individual runs, 1 = time series, 2 = look-up table

```{r}
set_options(simulation = 1)
```


