---
title: "introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(SCOPEr1)
```

This package runs SCOPE in R language. 

Sample workflow is below:

Step 1: install SCOPEr1 package from github
```{r}
devtools::install_github("SCOPEr", "kacebron")
```
Step 2: initiate run_scope to run a test verifying integrity of copy of SCOPE model
```{r}
run_scope("../../SCOPE/SCOPE.m")
```
Step 3: modify setoptions.csv using set_options()
``` {r}
set_options(verify = FALSE, simulation = 1)
```
Step 4: modify set_parameters_file.csv using set_paramFile()
``` {r}
set_paramFile(input = "input_data_default.csv")
```
Step 5: create an input directory (only for time series simulations)
```{r}
dir.name <- c("example_name")
dir.create(sprintf("../../SCOPE/input/dataset %s", dir.name))
```
Step 6: create an input filename
```{r}
input.filename <- "example_input_filename"
```
Step 7: 
