---
title: "introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(SCOPEr1)
```

This package runs SCOPE in R language. 

Sample workflow is below:

Step 1: install SCOPEr1 package from github
```{r}
devtools::install_github("kacebron/SCOPEr")
```
Step 2: initiate run_scope to run a test verifying integrity of copy of SCOPE model
```{r}
run_scope("../../SCOPE/SCOPE.m")
```
Step 3: modify setoptions.csv using set_options()
``` {r}
set_options(path = "../../SCOPE/input/setoptions.csv", verify = FALSE, simulation = 1)
```
Step 4: modify set_parameters_file.csv using set_paramFile()
``` {r}
set_paramFile(input = "input_data_default.csv")
```
Step 5: create an input directory (only for time series simulations)
```{r}
dir.name <- c("example_name")
dir.create(sprintf("../../SCOPE/input/dataset %s", dir.name))
```
Step 6: create an input filename
```{r}
input.filename <- "example_input_filename"
```
Step 7: set input/output names and add/delete column names for certain parameters inside filenames.csv
```{r}
set_filenames(simulation_name = dir.name, 
          dataset_dir = dir.name,
          meteo_ec_csv = input.filename,
          tts = FALSE) # when FALSE, this automatically computes solar zenith angle (tts) from the timezone, latitude and longitude provided inside the input_data_default.csv
```
Step 8: create duration and temporal resolution of time series
```{r}
start.time <- as.character("2012-07-03 00:00")
end.time <- as.character("2017-08-31 23:30")
span <- "30 mins"
```
Step 9: create constant parameters (this can be linked to some ground truth data)
```{r}
PCA.means <- read.csv("3_output_clean_data/PCA_groupings_mean.csv")

Cluster.no <- 3
    
par.constant <- c(PCA.means$ChlTot_ug_cm2_mean[Cluster.no], 
                      PCA.means$Carot_ug_cm2_mean[Cluster.no], 
                      PCA.means$anth_ug_cm2_mean[Cluster.no], 
                      PCA.means$dmc_g_per_cm2_mean[Cluster.no], 0.009, 0, 1.4, 6.5, -0.35, -0.15, PCA.means$Vcmax_mean[Cluster.no], 
      8, 0.1, 70, 0, 90)
    names(par.constant) <- c("Cab", "Cca", "Cant", "Cdm", "Cw", "Cs", 
      "N", "LAI", "LIDFa", "LIDFb", "Vcmax25", "BallBerrySlope",
      "BallBerry0","tts", 
      "tto", "psi")
```
Step 10: create variable parameters (still need to work on the bci meteo data)
```{r}
load(file="../bcipanama/3_output_clean_data/bci_ec_flux.Rda")
    par.variable.names <- c("Rs", "tair", "RH")
    par.variable <- bci_ec_flux[(bci_ec_flux$date >= start.time & 
      bci_ec_flux$date <= end.time 
      #& !is.na(bci_ec_flux$date)
      ), 
      par.variable.names]
    
    colnames(par.variable) <- c("Rin", "Ta", "RH")
```
Step 11: create a input variables for time series (Note: solar zenith and azimuth angle automatically computes based on time, lat and long)
```{r}
create_ts_input(start_time, end_time, span = span, run_nightTime = FALSE, 
              par_constant, par_variable,
              dir_name = paste0("../SCOPE/input/dataset ", dir.name), 
              filename = input.filename)
```
    
